Experimento Stella-Trump

### 2019-01-16 stella-trump.Rmd
REU2

logmaxmin <- lm(log_reco~treat, data = st) #Test tratamientos simultaneamente 
summary(logmaxmin)
#log(máximo/mínimo) ----
texreg::htmlreg(list(e1ad03,e1bd03,e2cd03), 
                custom.model.names = c("Condición A", "Condición B", "Condición C"),
                caption = "Log(máximo/mínimo)",
                custom.coef.names = c("(Intercepto)","Tratamiento"),
                caption.above = TRUE)
#Máximos/mínimo sin log ----
texreg::htmlreg(list(e1ad200,e1bd200,e2cd200), 
                custom.model.names = c("Condición A", "Condición B", "Condición C"),
                caption = "(máximo/mínimo) sin log",
                custom.coef.names = c("(Intercepto)","Tratamiento"),
                caption.above = TRUE)
```

@@

ggsave("C:/Users/JC/Dropbox/Investigación Trump/presentacion-alas/barplot3.png", barplot2,units = "cm", width = 20,height = 15, dpi = "retina")
```

@@

texreg::htmlreg(list(e1ab03,e1ac03,e2bc03), 
                custom.model.names = c("Condición A vs B", "Condición A vs C", "Condición B vs C"),
                caption = "Log(Ingreso Recomendado)",
                custom.coef.names = c("(Intercepto)","Tratamiento"),
                caption.above = TRUE)
```

@@

texreg::htmlreg(list(e1ad04,e1bd04,e2cd04,logOG), 
                custom.model.names = c("Condición A", "Condición B", "Condición C","Condiciones ABC"),
                caption = "Log(Gerente/Obrero)",
                custom.coef.names = c("(Intercepto)",
                                      "Tratamiento",
                                      "Tratamiento A",
                                      "Tratamiento B",
                                      "Tratamiento C"),
                caption.above = TRUE)

@@

texreg::htmlreg(list(e1ad04,logOGcov1,e1bd04,logOGcov2,e2cd04,logOGcov3), 
                custom.model.names = c("Modelo A", "Controles", "Modelo B","Controles", "Modelo C", "Controles"),
                caption = "Log(Gerente/Obrero)",
                custom.coef.names = c("(Intercepto)","Tratamiento información","Creencia Mundo Justo",
                                      "Centro", "Derecha/Centro Derecha", "Ninguno", "NS/NR", 
                                      "Log(Desigualdad percibida)"),
                caption.above = TRUE)

>>>>

logmaxmin <- lm(log_reco~treat, data = st) #Test tratamientos simultaneamente 
summary(logmaxmin)
#log(máximo/mínimo) ----
texreg::htmlreg(list(e1ad03,e1bd03,e2cd03), 
                custom.model.names = c("Condición A", "Condición B", "Condición C"),
                caption = "Log(máximo/mínimo)",
                custom.coef.names = c("(Intercepto)","Tratamiento"),
                caption.above = TRUE,
                file = "log_min_max.doc")
#Máximos/mínimo sin log ----
texreg::htmlreg(list(e1ad200,e1bd200,e2cd200), 
                custom.model.names = c("Condición A", "Condición B", "Condición C"),
                caption = "(máximo/mínimo) sin log",
                custom.coef.names = c("(Intercepto)","Tratamiento"),
                caption.above = TRUE,
                file = "slog_min_max.doc")
```

@@

ggsave("C:/Users/JC/Dropbox/Investigacion-Trump/presentacion-alas/barplot3.png", barplot2,units = "cm", width = 20,height = 15)
```

@@

texreg::htmlreg(list(e1ab03,e1ac03,e2bc03), 
                custom.model.names = c("Condición A vs B", "Condición A vs C", "Condición B vs C"),
                caption = "Log(Ingreso Recomendado)",
                custom.coef.names = c("(Intercepto)","Tratamiento"),
                caption.above = TRUE,
                file = "compare_treats.doc")
```

@@

texreg::htmlreg(list(e1ad04,e1bd04,e2cd04,logOG), 
                custom.model.names = c("Condición A", "Condición B", "Condición C","Condiciones ABC"),
                caption = "Log(Gerente/Obrero)",
                custom.coef.names = c("(Intercepto)",
                                      "Tratamiento",
                                      "Tratamiento A",
                                      "Tratamiento B",
                                      "Tratamiento C"),
                caption.above = TRUE,
                file = "C:/Users/JC/Dropbox/Investigacion-Trump/Resultados/tables/log_min_max.xls")

@@

texreg::htmlreg(list(e1ad04,logOGcov1,e1bd04,logOGcov2,e2cd04,logOGcov3), 
                custom.model.names = c("Modelo A", "Controles", "Modelo B","Controles", "Modelo C", "Controles"),
                caption = "Log(Gerente/Obrero)",
                custom.coef.names = c("(Intercepto)","Tratamiento información","Creencia Mundo Justo",
                                      "Centro", "Derecha/Centro Derecha", "Ninguno", "NS/NR", 
                                      "Log(Desigualdad percibida)"),
                caption.above = TRUE,
                reorder.coef = c(2:8,1),
                file = "C:/Users/JC/Dropbox/Investigacion-Trump/Resultados/tables/log_min_max_controls.xls")
